\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}
\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%% Redefines the elsarticle footer
%\makeatletter
%\def\ps@pprintTitle{%
% \let\@oddhead\@empty
% \let\@evenhead\@empty
% \def\@oddfoot{\it \hfill\today}%
% \let\@evenfoot\@oddfoot}
%\makeatother

% A modified page layout
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Assessing the neonicotinoid insecticide (imidacloprid) exposure-associated population decreasing risk for honeybees},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header


\usepackage[nomarkers]{endfloat}

\begin{document}
\begin{frontmatter}

  \title{Assessing the neonicotinoid insecticide (imidacloprid)
exposure-associated population decreasing risk for honeybees}
    \author[Some Institute of Technology]{Nan-Hung Hsieh}
   \ead{d99622005@ntu.edu.tw} 
  
    \author[A Institute of Technology]{Wei-Yu Chen}
   \ead{wychen@kmu.edu} 
  
    \author[B Institute of Technology]{Szu-Chieh Chen}
   \ead{scchen@csmu.edu} 
  
    \author[Another University]{Yi-Hsien Cheng}
   \ead{f98622020@ntu.edu.tw} 
  
    \author[Another University]{Chung-Min Liao\corref{c1}}
   \ead{cmliao@ntu.edu.tw} 
   \cortext[c1]{Corresponding Author}
      \address[Some Institute of Technology]{Department of Veterinary Integrative Biosciences, Texas A\&M University,
College Station 77845, Texas, USA}
    \address[A Institute of Technology]{Department of Biomedical Science and Environmental Biology, Kaohsiung
Medical University, Kaohsiung 80708, Taiwan, ROC}
    \address[B Institute of Technology]{Department of Public Health, Chung Shan Medical University, Taichung
40242, Taiwan, ROC}
    \address[Another University]{Department of Bioenvironmental Systems Engineering, National Taiwan
University, Taipei 10617, Taiwan, ROC}
  
  \begin{abstract}
  This is the abstract.
  
  It consists of two paragraphs.
  \end{abstract}
   \begin{keyword} Honeybees, Population dynamics, Ecotoxicology, Imidacloprid,
Probabilistic risk assessment \sep \end{keyword}
 \end{frontmatter}

\emph{Text based on elsarticle sample manuscript, see
\url{http://www.elsevier.com/author-schemas/latex-instructions\#elsarticle}}

\section{1. Introduction}\label{introduction}

\section{2. Materials and Methods}\label{materials-and-methods}

\paragraph{2.1. Study framework and
data}\label{study-framework-and-data}

\begin{verbatim}
To assess
\end{verbatim}

Taking into account

\paragraph{2.2. Effect and exposure
analysis}\label{effect-and-exposure-analysis}

\paragraph{2.3. Risk characterization}\label{risk-characterization}

\paragraph{2.4. Uncertainty and statistical
analysis}\label{uncertainty-and-statistical-analysis}

\section{3. Results}\label{results}

\paragraph{3.1. Dose--mortality
assessment}\label{dosemortality-assessment}

\paragraph{3.2. Predicted environmental
exposure}\label{predicted-environmental-exposure}

\paragraph{3.3. Risk predictions}\label{risk-predictions}

\paragraph{3.4. Sensitivity analysis}\label{sensitivity-analysis}

\section{4. Discussion}\label{discussion}

\section{5. Conclusions}\label{conclusions}

\section{The Elsevier article class}\label{the-elsevier-article-class}

\paragraph{Installation}\label{installation}

If the document class \emph{elsarticle} is not available on your
computer, you can download and install the system package
\emph{texlive-publishers} (Linux) or install the LaTeX~package
\emph{elsarticle} using the package manager of your TeX~installation,
which is typically TeX~Live or MikTeX.

\paragraph{Usage}\label{usage}

Once the package is properly installed, you can use the document class
\emph{elsarticle} to create a manuscript. Please make sure that your
manuscript follows the guidelines in the Guide for Authors of the
relevant journal. It is not necessary to typeset your manuscript in
exactly the same way as an article, unless you are submitting to a
camera-ready copy (CRC) journal.

\paragraph{Functionality}\label{functionality}

The Elsevier article class is based on the standard article class and
supports almost all of the functionality of that class. In addition, it
features commands and options to format the

\begin{itemize}
\item
  document style
\item
  baselineskip
\item
  front matter
\item
  keywords and MSC codes
\item
  theorems, definitions and proofs
\item
  lables of enumerations
\item
  citation style and labeling.
\end{itemize}

\section{Front matter}\label{front-matter}

The author names and affiliations could be formatted in two ways:

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Group the authors per affiliation.
\item
  Use footnotes to indicate the affiliations.
\end{enumerate}

See the front matter of this document for examples. You are recommended
to conform your choice to the journal you are submitting to.

\section{Bibliography styles}\label{bibliography-styles}

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX~to generate your bibliography and include DOIs
whenever available.

Here are two sample references: Feynman and Vernon Jr. (1963; Dirac
1953).

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Dirac1953888}{}
Dirac, P.A.M. 1953. ``The Lorentz Transformation and Absolute Time.''
\emph{Physica} 19 (1---12): 888--96.
doi:\href{https://doi.org/10.1016/S0031-8914(53)80099-6}{10.1016/S0031-8914(53)80099-6}.

\hypertarget{ref-Feynman1963118}{}
Feynman, R.P, and F.L Vernon Jr. 1963. ``The Theory of a General Quantum
System Interacting with a Linear Dissipative System.'' \emph{Annals of
Physics} 24: 118--73.
doi:\href{https://doi.org/10.1016/0003-4916(63)90068-X}{10.1016/0003-4916(63)90068-X}.

\end{document}


